Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-26 manuscript.Rmd
Code cleaning. All functional.

```{r tableArticleSummary, eval=TRUE, cache=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
    select(-attributes, -record)

```
```{r}

@@

plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count, group=1)) + 
    theme_bw() + 
    geom_line(colour=cp[4], size = 1, alpha = .80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Unique Journal Titles") + 
    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

@@

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Number of Articles Published") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

```{r plotSmallMultiples, cache=FALSE}
# Remove 2014 & 2015

@@

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    theme_bw() + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101", alpha=.60) + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Number of Authors") +
    xlab("") +
    labs(size = "SD") +
    labs(colour = NULL) + 
    scale_colour_manual(values = c("#fdb864", "#e66101")) +
    theme(axis.title.x = element_text(vjust=-0.5), 
          axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") + 
       theme(title = element_text(size = 10))

@@

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99", alpha = .60) + 
    theme_bw() + 
    theme(title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    ylab("Number of Pages") +
    xlab("") +
    labs(size = "SD") +
     labs(colour = NULL) +   
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom")

@@

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT"))

@@

stacked.plot <- ggplot(stacked.df, 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) +
    theme_bw() +
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
    theme(  legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Number of Articles") + 
    xlab("Year") + 
    labs(fill = "") +
    scale_y_continuous(breaks = seq(0,90, 10)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

@@

evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
    theme_bw() +
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .03, .005))
```

@@

df1 <- df

@@

```{r plotEBPstackedBar}
pareto.df <- df1 %>% group_by(journal) %>% 
    summarize(EBP.counts = sum(N)) %>% 
    arrange(desc(EBP.counts)) %>%
    ungroup() %>%
    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
    mutate(cumSum = cumsum(percentTotal)) %>%
    slice(1:16)

@@

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity", alpha=.60) +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 3) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) +
    theme(legend.position = c(.65,.7),  legend.title=element_blank(), legend.background = element_rect(fill="transparent"))
```

@@

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point(colour="grey40") +
    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
            panel.margin = unit(0,"null")) + 
    ylab(NULL) +
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 3) +
    xlim(c(0, .5))

>>>>

```{r summarySetUp, eval=TRUE, cache=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
    select(-attributes, -record)
```

```{r  plot01_JournalsArticles, cache=TRUE}
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

@@

plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count, group=1)) + 
    theme_bw() + 
    geom_line(colour=cp[4], size = 1, alpha = .80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))

@@

plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
    theme_bw() + 
    geom_line(colour=cp[2], size = 1, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
```

```{r plot02_SmallMultiples, cache=TRUE}
# Remove 2014 & 2015

@@

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    theme_bw() + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101", alpha=.60) + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Number of Authors") +
    xlab("") +
    labs(size = "SD = ") +
    labs(colour = NULL) + 
    scale_colour_manual(values = c("#fdb864", "#e66101")) +
    theme(axis.title.x = element_text(vjust=-0.5), 
          axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") + 
       theme(title = element_text(size = 10)) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) +
    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))

@@

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99", alpha = .60) + 
    theme_bw() + 
    theme(title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    ylab("Number of Pages") +
    xlab("") +
    labs(size = "SD = ") +
     labs(colour = NULL) +   
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) +
    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))

@@

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSys Rev", "Quasi-experimental", "RCT"))

@@

stacked.plot <- ggplot(stacked.df, 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) +
    theme_bw() +
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
    theme(  legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Number of Articles") + 
    xlab("Year") + 
    labs(fill = "") +
    scale_y_continuous(breaks = seq(0,90, 10)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) +
    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size =8),
    title = element_text(size = 10), plot.title=element_text(size=10)) +
    theme(legend.text = element_text(size = 8))
```

@@

evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
    theme_bw() +
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .03, .005)) +
    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size =8),
    title = element_text(size = 8), plot.title=element_text(size=8)) +
    theme(legend.text = element_text(size = 8))
```

@@

@@

```{r plotEBPstackedBar}

df1 <- df
pareto.df <- df1 %>% group_by(journal) %>% 
    summarize(EBP.counts = sum(N)) %>% 
    arrange(desc(EBP.counts)) %>%
    ungroup() %>%
    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
    mutate(cumSum = cumsum(percentTotal)) %>%
    slice(1:16)

@@

journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
    geom_bar(aes(fill = studyType), stat = "identity", alpha=.60) +
    coord_flip() +
    theme_bw() + 
    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 2.5) +
    labs(x = "Journal", y = "N") +
    ylim(c(0, 150)) +
    scale_fill_manual(values = cp) +
    theme(legend.position = c(.65,.7),  legend.title=element_blank(), 
          legend.background = element_rect(fill="transparent")) +
    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) +
    theme(legend.text = element_text(size = 8))
```

@@

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point(colour="grey40") +
    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
            panel.margin = unit(0,"null")) + 
    ylab(NULL) +
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 2.5) +
    xlim(c(0, .5))  +
    theme(axis.text.x = element_text(size=8),  
    title = element_text(size = 8), plot.title=element_text(size=8)) +
    theme(legend.text = element_text(size = 8))
